---
title: "Cas_usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cas_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(squirrels)
```


# Use Case: Filtering and Saving Squirrel Data

This vignette demonstrates how to use the functions in the package to filter squirrel data based on their integrity and save the results into separate CSV files.

## Loading the Data

Start by loading the demo squirrel data included in the package.
```{r}
data("data_demo_squirrels")
```



## Filtering the Data

Next, we apply the `filter_squirrels_data_based_on_integrity` function to filter the data based on their integrity. This function divides the data into three categories: valid, invalid, and missing.
```{r}
filtered_data <- filter_squirrels_data_based_on_integrity(data_demo_squirrels)
filtered_data
```



## Saving the Filtered Data

Create a temporary directory to save the filtered data and use the `save_as_csv` function to save each category into separate CSV files.
```{r}
output_dir <- tempfile()
dir.create(output_dir)

save_as_csv(
  df = filtered_data$df_valid_data,
  path = file.path(output_dir, "valid_data.csv")
)

save_as_csv(
  df = filtered_data$df_invalid_data,
  path = file.path(output_dir, "invalid_data.csv")
)

save_as_csv(
  df = filtered_data$df_missing_data,
  path = file.path(output_dir, "missing_data.csv")
)
```



